#Data analyses and figure creation for the YouTube Stroop Experiment

###William H. Knapp III

##Introduction

This file was used to analyze data from my
[YouTube Stroop Experiment](https://www.youtube.com/watch?v=djUgM2GjudE).
All materials including consent, experimental tasks, and debriefing can
be accessed following the previous link and following the links embedded
within the video. **NOTE**: the links embedded in the vidoes are not
available on some mobile devices that lack support for flash (e.g. some
iPhones and iPads).

These data represent observations from 53 participants who reported
participating in existing conditions and emailed me their data. 1
participant reported participating in condition 6, when there were
only 4 conditions. This individual was excluded from this data set
(see preprocessing.R).

Although a number of variables are included in the raw data, only the
variables representing subject, time in the video they completed the
Stroop task (i.e. naming the color of the presented words), and
congruence (i.e. congruent: color name matched the name of the word;
and incongruent: color name didn't match the name of the word) were
of primary interest. These data were analyzed and included in the 
poster and presentation. Additional analyses were performed, but not
included in these forms. These analyses appear at the end of this
document.

##Preparing data for analysis

First we need to read in the data.

```{r}
d<-read.csv("rawdat.csv")
```

Now, let's look for any impossible reported times. The Stroop stimuli
appeared in the videos at 29.0 seconds, so any reported times of 29 or
less reflect an error. We'll identify the participants who made such
errors and eliminate them from the data.

```{r}
badsubs<-unique(d$sub[d$rt<=29])
d<-d[!(d$sub %in% badsubs),]
```

Now that we only have meaningful data, we'll transform the 
quarter, group, and subject variables into factor variables.

```{r}
d$quarter<-as.factor(d$quarter)
d$group<-as.factor(d$group)
d$sub<-as.factor(d$sub)
```

##Primary Analysis

Now we'll use a paired t-test to determine whether the Stroop
effect occured for the participants when YouTube was the experimental
medium. We'll also use a one-tailed test as the Stroop effect
is demonstrated when participants are slower to identify colors
in the presence of incongruent color words (e.g. the word "BLUE"
appearing in the color red) than they are to identify colors in
the presence of congruent color words (e.g. the word "BLUE" appearing
in the color blue).

```{r}
t<-t.test(d$rt[d$congruence=="Incongruent"],
       d$rt[d$congruence=="Congruent"],
       paired=TRUE,
       alternative="greater")
t
```

Indeed, participants in this YouTube experiment showed the typical
Stroop effect, t(`r t$parameter[[1]]`) = `r sprintf("%.2f",t$statistic[[1]])`,
p `r ifelse(t$p.value[[1]]>.0001, sprintf("= %.4f",t$p.value[[1]]),"< .001")`.
They were slower in the incongruent than they were in the congruent condition.

##Figure

To visualize this, I'm going to create a box plot comparing
reported times for the congruent and incongruent conditions.

```{r, eval=FALSE}
library(ggplot2)
```
```{r,include=FALSE}
library(ggplot2)
```
```{r}
#Create and edit the box plot
f<-ggplot(d, aes(x=congruence,y=rt))+
  geom_boxplot()+
  guides(fill=FALSE)+
  labs(x="Word Color Congruence", y="Time Completed (seconds)")+
  scale_x_discrete(breaks=c("Congruent","Incongruent"),labels=c("Congruent","Incongruent"))+
  theme(axis.title.x=element_text(size=20,face="bold",vjust=-.8))+
  theme(axis.title.y=element_text(size=20,face="bold",vjust=1.5))+
  theme(axis.text.x=element_text(size=18,face="bold",color="black"))+
  theme(axis.text.y=element_text(size=18,face="bold",color="black"))+
  theme(panel.border=element_blank(), axis.line=element_line())+
  theme(panel.grid.major.x=element_blank())+
  theme(panel.grid.major.y=element_line(color="darkgrey"))+
  theme(panel.grid.minor.y=element_blank())

#Plot the box plot
f
```

I'll use this figure in the poster, so I need to save it.

```{r}
ggsave(filename="fig1.png",width=15,height=15, units="cm",dpi=300)
```

##Supplementary Analyses

The following analyses were performed to get a better sense of the data,
but they will not be included in the poster.

Let's see if the order of conditions affected reported times or
interacted with congruence.

```{r}
summary(aov(rt~congruence*order+Error(sub/congruence), data=d))
```

Nope, order didn't matter.

Let's see how many of the participants that were included in the previous
analyses demonstrated the effect.

```{r}
showing<-sum(d$rt[d$congruence=="Incongruent"]>d$rt[d$congruence=="Congruent"])
n<-length(d$rt[d$congruence=="Incongruent"])
showing/n
```

`r sprintf("%.1f",showing/n*100)`% of the participants (i.e. `r showing`/`r n`)
demonstrated the effect.

##Summary

For powerful effects, YouTube appears to be a viable experimental
platform.